Data Preparation

### 2019-01-10 Data Preparation.Rmd

```{r overview}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))

course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP")
course_code <- paste(course_code, collapse = "|")

content_to_exclude <- c("^Core Courses \\(COR\\)",
                        "^Humanities \\(HUM\\)",
                        "^Sciences \\(SCI\\)",
                        "^Social Sciences \\(SSC\\)",
                        "^Skills Trainings \\(SKI\\)",
                        "^Projects \\(PRO\\)",
                        "^Undergraduate Research \\(UGR\\)",
                        "Appendix")
content_to_exclude <- paste(content_to_exclude, collapse = "|")

@@

print(d_description)
```

#### Extracting Descriptions
Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews. The description section contains a brief description (200-500 words) of the content of the course. To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends. The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`. The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`). Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost overviews. A handful overviews do not contain a *Literature* section. For these, the section *Instructional Format* marks the end of the description section.
```{r description}
# Setup
symbol_to_line <- c("\r\n", "\n")
symbol_to_line <- paste(symbol_to_line, collapse = "|")

start_descrip <- c("^Description", "^Course Description")
start_descrip <- paste(start_descrip, collapse = "|")

end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
                   "^Required Litera", "^ Literature$", "Literature \\(all")
end_descrip   <- paste(end_descrip, collapse = "|")

@@

  overview_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
  line_start    <- grep(pattern = start_descrip, x = overview_line) + 1
  line_end      <- grep(pattern = end_descrip  , x = overview_line) - 1

  # for overviews w/o Literature section, find section Instructional Format.
  if(is_empty(line_end)){
    line_end <- grep(pattern = "^Instructional format$", x = overview_line) - 1
    print(paste("line_end irregular for", d_description$Code[course],
                "in catalogue", d_description$`Calendar Year`[course]))
    } # close if-statement

  description <- paste(overview_line[line_start : line_end], collapse = " ")

@@

print(d_description)
```

>>>>

```{r extracting overview}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))

course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
  paste(collapse = "|")

content_to_exclude <- c("^Core Courses \\(COR\\)",
                        "^Humanities \\(HUM\\)",
                        "^Sciences \\(SCI\\)",
                        "^Social Sciences \\(SSC\\)",
                        "^Skills Trainings \\(SKI\\)",
                        "^Projects \\(PRO\\)",
                        "^Undergraduate Research \\(UGR\\)",
                        "Appendix") %>%
  paste(collapse = "|")

@@

rm(n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
   page, current_page, following_page, current_page_content, following_page_content,
   course_overview, Code, year)
print(d_description)
```

#### Extracting Descriptions
Since the overviews contain a lot of information that does not interest us, we extract the description section of the overviews. The description section contains a brief description (200-500 words) of the content of the course. To accomplish this, for each overview, we need to identify the line where the description starts and the line where it ends. The description section is always preceeded by a header saying *Description* or *Course Description* (`start_descrip`), making it relatively easy to find the starting line of the decription section with `grep`. The description section is usually followed by the literature section which starts with header saying *Literature*, *Recommended Literature* or similar (see `end_descrip`). Using `grep` together with `end_descrip`, we can again identify the ending line of the description section of almost overviews. A handful overviews do not contain a *Literature* section. For these, the section *Instructional Format* marks the end of the description section.
```{r extracting description}
# Setup
symbol_to_line <- c("\r\n", "\n") %>%
  paste(collapse = "|")

start_descrip <- c("^Description", "^Course Description") %>%
  paste(collapse = "|")

end_descrip   <- c("^Literature$", "^Recommended Literature", "^ Required Litera",
                   "^Required Litera", "^ Literature$", "Literature \\(all") %>%
  paste(collapse = "|")

@@

  overview_by_line <- strsplit(x = toString(overview), split = symbol_to_line)[[1]]
  line_start    <- grep(pattern = start_descrip, x = overview_by_line) + 1
  line_end      <- grep(pattern = end_descrip  , x = overview_by_line) - 1

  # for overviews w/o Literature section, find section Instructional Format.
  if(is_empty(line_end)){
    line_end <- grep(pattern = "^Instructional format$", x = overview_by_line) - 1
    print(paste("line_end irregular for", d_description$Code[course],
                "in catalogue", d_description$`Calendar Year`[course]))
    } # close if-statement

  description <- paste(overview_by_line[line_start : line_end], collapse = " ")

@@

rm(symbol_to_line, start_descrip, end_descrip,
   course, overview, overview_by_line, line_start, line_end, description)
print(d_description)
```
